---
title: "HW4"
output: html_document
---

In this assignment you will produce a dashboard that lets readers explore data from the World Value Study
(WVS).

Your submission will again be a GitHub repo that will include the README and a script that
runs and creates the app.

1. Download the World Value Study (wave 6) from here: http://www.worldvaluessurvey.org/WVSDocumentationWV6.jsp



```{r}
library(tidyverse)
library(shiny)

load("C:\\Users\\Owner\\SURV675_HW4\\WV6_Data_R_v20201117.rdata")

dat.work <- WV6_Data_R_v20201117 

#Country
Country <- dat.work %>% 
  select(V2) %>%
  mutate(V2 = as.factor(case_when(
      V2 == 12  ~ "Algeria",
      V2 == 31  ~ "Azerbaijan",
      V2 == 32  ~ "Australia",
      V2 == 36  ~ "Bahrain",
      V2 == 48  ~ "Armenia",
      V2 == 51  ~ "Brazil",
      V2 == 76  ~ "Belarus",
      V2 == 112 ~ "Chile",
      V2 == 152 ~ "China",
      V2 == 156 ~ "Taiwan",
      V2 == 158 ~ "Colombia",
      V2 == 170 ~ "Cyprus",
      V2 == 196 ~ "Ecuador",
      V2 == 218 ~ "Estonia",
      V2 == 233 ~ "Georgia",
      V2 == 268 ~ "Palestine",
      V2 == 275 ~ "Germany",
      V2 == 276 ~ "Ghana",
      V2 == 288 ~ "Haiti",
      V2 == 332 ~ "Hong Kong",
      V2 == 344 ~ "India",
      V2 == 356 ~ "Iraq",
      V2 == 368 ~ "Japan",
      V2 == 392 ~ "Kazakhstan",
      V2 == 398 ~ "Jordan",
      V2 == 400 ~ "South Korea",
      V2 == 410 ~ "Kuwait",
      V2 == 414 ~ "Kyrgyzstan",
      V2 == 422 ~ "Lebanon",
      V2 == 434 ~ "Libya",
      V2 == 458 ~ "Malaysia",
      V2 == 484 ~ "Mexico",
      V2 == 504 ~ "Morocco",
      V2 == 554 ~ "New Zealand",
      V2 == 566 ~ "Nigeria",
      V2 == 586 ~ "Pakistan",
      V2 == 604 ~ "Peru", 
      V2 == 608 ~ "Philippines",
      V2 == 616 ~ "Poland",
      V2 == 642 ~ "Romania",
      V2 == 643 ~ "Russia",
      V2 == 646 ~ "Rwanda",
      V2 == 702 ~ "Singapore",    
      V2 == 710 ~ "South Africa",
      V2 == 716 ~ "Zimbabwe",
      V2 == 752 ~ "Sweden",
      V2 == 764 ~ "Thailand",  
      V2 == 788 ~ "Tunisia",
      V2 == 792 ~ "Turkey",
      V2 == 804 ~ "Ukraine",
      V2 == 818 ~ "Egypt",
      V2 == 840 ~ "United States",
      V2 == 858 ~ "Uruguay",
      V2 == 860 ~ "Uzbekistan",
      V2 == 887 ~ "Yemen"))
    ) %>% 
  rename(Country = V2) 


#Democracy 
dat.clean <- dat.work %>% 
  rename(
    D_Choice = V228I, 
    D_Threatened = V228H, 
    D_Rich = V228G, 
    D_Fair = V228F, 
    D_Journalists = V228E, 
    D_Bribed = V228D, 
    D_BiasedTV = V228C, 
    D_Opponents = V228B, 
    D_Count = V228A, 
    
    N_Paper = V217,
    N_Magazine = V218,
    N_TV = V219, 
    N_Radio = V220, 
    N_CellPhone = V221, 
    N_Email = V222, 
    N_Internet = V223,
    N_Talking = V224, 
    
    S_LifeBetter = V192, 
    S_Oppertunities = V193, 
    S_Faith = V194, 
    S_Morals = V195, 
    S_Unimportant = V196, 
    S_World = V197
  ) 

dat.clean <- cbind(dat.clean, Country)

dat.clean <- dat.clean %>% drop_na(Country)

Dat <- dat.clean %>% 
  select(
    Country,
    D_Choice, 
    D_Threatened, 
    D_Rich, 
    D_Fair, 
    D_Journalists, 
    D_Bribed, 
    D_BiasedTV, 
    D_Opponents, 
    D_Count,
    N_Paper,
    N_Magazine,
    N_TV, 
    N_Radio, 
    N_CellPhone, 
    N_Email, 
    N_Internet,
    N_Talking,
    S_LifeBetter, 
    S_Oppertunities, 
    S_Faith, 
    S_Morals, 
    S_Unimportant, 
    S_World)


# Creating Smaller Datasets 
Dem <- dat.clean %>% 
  select(
    Country,
    D_Choice, 
    D_Threatened, 
    D_Rich, 
    D_Fair, 
    D_Journalists, 
    D_Bribed, 
    D_BiasedTV, 
    D_Opponents, 
    D_Count
  )

News <- dat.clean %>% 
  select(
    Country,
    N_Paper,
    N_Magazine,
    N_TV, 
    N_Radio, 
    N_CellPhone, 
    N_Email, 
    N_Internet,
    N_Talking
  )

Sci <- dat.clean %>% 
  select(
    Country,
    S_LifeBetter, 
    S_Oppertunities, 
    S_Faith, 
    S_Morals, 
    S_Unimportant, 
    S_World )
```
```{r}
Long.News <- News %>%
  pivot_longer(
    cols = 2:9,
    names_to = "Variable",
    values_to = "Response"
  )

# Get total counts per country
cont.total <- News %>%
  count(Country) %>%
  deframe()

# Calculate proportions for each response value (1 to 5) for all countries
AllComb <- Long.News %>%
  group_by(Country, Variable, Response) %>%
  count() %>%
  mutate(Prop = round(n / cont.total[Country], 4)) %>%
  select(Country, Variable, Response, Prop) %>%
  pivot_wider(names_from = Response, values_from = Prop, names_prefix = "Prop") 

# Pivot long then wide for each country
AllComb_Fin <- AllComb %>%
  pivot_longer(
    cols = starts_with("Prop"),
    names_to = "Response",
    values_to = "Value"
  ) %>%
  mutate(Response = as.integer(gsub("Prop", "", Response))) %>%
  pivot_wider(
    names_from = Variable,
    values_from = Value
  )

AllComb_Fin

```


About Section: 
  a. Overview: here you can say what is the aim of the app and guide the user in how to navigate it (10%)
  b. Exploring attitudes to democracy (V228A-V228I) (20%)
  c. Exploring news consumption (V217-V224) (20%)
  d. Exploring attitudes to science (V192-197) (20%)
  
Sections b, c and d all have three things inside:
  • plot the averages (proportions by category for news) of the questions in that section for the country
    selected (i.e., if they select Algeria shows the graph just for Algeria)
  • a table with the averages (proportions by category for news) of the questions in that section for the
    country selected
  • a similar table as above but with the information on the entire WVS sample 
  
  
Welcome! This app is designed to let you explore data from the World Value Study's 2006 Wave. 

Please use the sidebar menu to navigate through the different pages. Within the Graphs & Tables page, you will find Graphs, Tables, and All Countries. The Graphs and Tables sections will show you three different options: the average attitudes towards democracy, average news consumption, and the average attitudes towards science for the country you select. The All Countries section will show you the same information but for all countries in the dataset. Please note that some countries may not produce graphs and tables for all three options due to one or more question not being asked in that county's survey. 

The Data page will display the full dataset used for this app. To differentiate between the different sections, variables starting with "D_" are the democracy questions, "N_" are news consumption, and "S_" are science. 

"Click for Github Repository" will immediately open and navigate to the Github repository for this project where more information on the creation of this app can be located. 

Citation for data used: 
Inglehart, R., C. Haerpfer, A. Moreno, C. Welzel, K. Kizilova, J. Diez-Medrano, M. Lagos, P. Norris, E. Ponarin & B. Puranen et al. (eds.). 2018. World Values Survey: Round Six - Country-Pooled Datafile. Madrid, Spain & Vienna, Austria: JD Systems Institute & WVSA Secretariat. doi.org/10.14281/18241.8




# Section B
## Attitudes towards Democracy
```{r}
#  • plot the averages (proportions by category for news) of the questions in that section for the country
#    selected (i.e., if they select Algeria shows the graph just for Algeria) 
Dat %>% 
  group_by(Country) %>%
  summarise_all(max, na.rm = T)

#  • a table with the averages (proportions by category for news) of the questions in that section for the
#    country selected
#  • a similar table as above but with the information on the entire WVS sample (*static?*)
    
#The results in sections b, c and d should change depending on the country input (except the last table in
#each section which is the same for all the countries).
```

# Section C
## News Consumption
```{r}
#  • plot the averages (proportions by category for news) of the questions in that section for the country
#    selected (i.e., if they select Algeria shows the graph just for Algeria)
News %>% 
  filter(Country == "Algeria") %>% 
  select(-Country) %>% 
  summarise_all(mean, na.rm = TRUE) 

News %>%
  ggplot(aes(time, y = health)) +
    geom_point(alpha = 0.15,
      position = position_jitter(width = .48, height = .45), 
      color = "deepskyblue4") +
    stat_summary(aes(group = 1), fun = mean,
      geom = "smooth", 
      color = "goldenrod1",
      linetype = 1,
      linewidth = 3) +
  theme_classic() +
    labs(x = "Time", y = "Health Rating",
        title = "Figure 1. 
        Average Change of Health Ratings Over Time",
        caption = "Data from HRS Waves '96, '98 & '00")
#  • a table with the averages (proportions by category for news) of the questions in that section for the
#    country selected
#  • a similar table as above but with the information on the entire WVS sample (*static?*)
    
#The results in sections b, c and d should change depending on the country input (except the last table in
#each section which is the same for all the countries).
```



# Section D
## Attitudes towards Science
```{r}
#  • plot the averages (proportions by category for news) of the questions in that section for the country
#    selected (i.e., if they select Algeria shows the graph just for Algeria)
#  • a table with the averages (proportions by category for news) of the questions in that section for the
#    country selected
#  • a similar table as above but with the information on the entire WVS sample (*static?*)
    
#The results in sections b, c and d should change depending on the country input (except the last table in
#each section which is the same for all the countries).
```


  a. Overview: here you can say what is the aim of the app and guide the user in how to navigate it (10%)
  b. Exploring attitudes to democracy (V228A-V228I) (20%)
  c. Exploring news consumption (V217-V224) (20%)
  d. Exploring attitudes to science (V192-197) (20%)
  
Sections b, c and d all have three things inside:
  • plot the averages (proportions by category for news) of the questions in that section for the country
    selected (i.e., if they select Algeria shows the graph just for Algeria)
  • a table with the averages (proportions by category for news) of the questions in that section for the
    country selected
  • a similar table as above but with the information on the entire WVS sample (*static?*)

The results in sections b, c and d should change depending on the country input (except the last table in
each section which is the same for all the countries).

3. Make the tables and figures interactive (10%)

4. Presentation (10%). Tables and graphs are easy to read. Overview section and GitHub README
are well written and useful.

5. Publish app on www.shinyapps.io (10%). Include the link to the app in the readme file.


Top tips
• You might want to separate the process of cleaning the data and the app. As such, you might want
to make a R script for all the preparation that saves all the objects you need and a script that just
includes the things needed to run the shiny app.
• You might want to prepare all the graphs and tables in R before putting them in Shiny to make sure
they work.
• You might want to consider using Shinydashboard to help organize the app and make the different tabs.
You can also check out this link: https://shiny.rstudio.com/articles/dashboards.html
• You might want to make reactives that summarizes the country level information needed for the plots
and tables.
• To make tables interactive use dataTableOutput/renderDataTable. For interactive graphs use
renderPlotly/plotlyOutput. On how to make a ggplot into a shiny plot check out this link:
https://stackoverflow.com/questions/37663854/convert-ggplot-object-to-plotly-in-shiny-application
• It is easy to publish a shiny app from rstudio. After you run the app just press the “publish” button.
You will need to make an account on: https://www.shinyapps.io/



